Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-11 providence/sections/workload.tex
typo

\textbf{Misleading SO Risk Measures.} As we consider the idea of misleading samples, it is noteworthy that SO \BRAVO suffers from a different and unique type of misleading result.

>>>>

\textbf{Misleading SO \BRAVO sequences.} As we consider the idea of misleading samples, it is noteworthy that SO \BRAVO suffers from a different and unique type of misleading result.
